The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-19 Paper.Rmd
adding comment about 3rd npa stat

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (KC) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}
<!--***DAN: Shya, I like the grey color of your points on the above figure, 
but I prefer the 
solid plotting symbols and the size of plotting symbols used on the new 
pedagogical figure that I made. Can you please change the code of both figures
so we get grey, with the plotting symbols I used, on both plots? Likeiwse for the 
new figure produced in ./ThirdPedagogFig.R, please. It will be
good to use the same points, for consistency. Don't worry at this stage about
making other figures, other than these three, consistent.-->

@@

We also defined the statistic $\Ps_{l_b,u_b}$ (Appendix \ref{SM-nonparam_stats}), 
which has a similar 
interpretation to $\cor_{l_{b_k},u_{b_k}}(u,v)$; we use both statistics 
because in some instances $\Ps_{l_b,u_b}$ appears to have more power to
reveal tail dependence than does $\cor_{l_{b_k},u_{b_k}}(u,v)$. 
<!--***DAN: need to make this a bit more precise, perhaps just enough to cite one of the supp mat sections where tests are done of these stats, but you need to review the tests first and what they show-->
Our third statistic, $\Dsq_{l_b,u_b}(u,v)$, is the average squared 
distance between points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ and the line $v=u$.
<!--***DAN: Shyamolina, is this actually right, i.e., did we use the average, or did we 
use the sum divided by n? Whichever way we did it is OK, but please check the code and revise the above 
text if necessary and insert a comment answering this comment. I tried to check this, myself, 
but I was having a hard time finding where the statistics are implemented. Please also
indicate in your response comment what line of what file has the implementation of these
statistics.-->
Unlike $\cor_{l_b,u_b}$ and 
$\Ps_{l_b,u_b}$, which are large when points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ cluster close to the line $v=u$, $\Dsq_{l_b,u_b}$ is 
small in that case. 
Thus large values of $\cor_{l_b,u_b}$ and $\Ps_{l_b,u_b}$ indicate strong 
dependence in the portions of the distributions of $u$ and $v$ given by 
the bounds, whereas small values of 
$\Dsq_{l_b,u_b}$ indicate strong dependence.

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption{(A-C) Data generated using the BB1 copula (Methods) with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (Methods), but the same 
Kendall correlation (KC) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column of panels.\label{fig_cop_pedag}}
\end{center}
\end{figure}
<!--***DAN: Shya, I like the grey color of your points on the above figure, 
but I prefer the 
solid plotting symbols and the size of plotting symbols used on the new 
pedagogical figure that I made. Can you please change the code of both figures
so we get grey, with the plotting symbols I used, on both plots? Likeiwse for the 
new figure produced in ./ThirdPedagogFig.R, please. It will be
good to use the same points, for consistency. Don't worry at this stage about
making other figures, other than these three, consistent.
***Shya: Done.-->

@@

We also defined the statistic $\Ps_{l_b,u_b}$ (Appendix \ref{SM-nonparam_stats}), 
which has a similar 
interpretation to $\cor_{l_{b_k},u_{b_k}}(u,v)$; we use both statistics 
because in some instances $\Ps_{l_b,u_b}$ appears to have more power to
reveal tail dependence than does $\cor_{l_{b_k},u_{b_k}}(u,v)$. 
<!--***DAN: need to make this a bit more precise, perhaps just enough to cite one of the supp mat sections where tests are done of these stats, but you need to review the tests first and what they show-->
Our third statistic, $\Dsq_{l_b,u_b}(u,v)$, is the average squared 
distance between points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ and the line $v=u$.
<!--***DAN: Shyamolina, is this actually right, i.e., did we use the average, or did we 
use the sum divided by n? Whichever way we did it is OK, but please check the code and revise the above 
text if necessary and insert a comment answering this comment. I tried to check this, myself, 
but I was having a hard time finding where the statistics are implemented. Please also
indicate in your response comment what line of what file has the implementation of these
statistics.
***Shya: In code we used the sum of squared distances divided by n(=number of points lying within two boundaries) which I think okay to be called as "average-squared distance" or average of squared distances between points within the two boundaries.
Reference : CopulaFunctions_flexible.R file, line 24.-->
Unlike $\cor_{l_b,u_b}$ and 
$\Ps_{l_b,u_b}$, which are large when points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ cluster close to the line $v=u$, $\Dsq_{l_b,u_b}$ is 
small in that case. 
Thus large values of $\cor_{l_b,u_b}$ and $\Ps_{l_b,u_b}$ indicate strong 
dependence in the portions of the distributions of $u$ and $v$ given by 
the bounds, whereas small values of 
$\Dsq_{l_b,u_b}$ indicate strong dependence.
